---
title: "01-Demographic"
output: html_notebook
---

## Aim

Determine the final sample and make the demographic table.

## ============ PART 1
## Prepare Data

```{r}
rm(list=ls())
library(data.table)
wcst <- fread("./wcst_short.csv")

dat <- wcst[, .(sex, age_group,age, Number_Correct, Number_PerseverativeResponse, Number_PerseverativeError, Number_NonPerseverativeError, Number_ConceptualLevelResponse, Number_Category, Number_FailureToMaintainSet)]

setnames(dat, old = names(dat)[4:10], c('TC', 'PR', 'PE', 'NPE', 'CLR', 'CAT', 'FMS'))

dat[, sex:=factor(sex, levels = c("female","male"), labels = c("Female", "Male"))]
dat[, age_group:=factor(age_group, levels = c("young","old"), labels = c("Young", "Old"))]
#setnames(dat, c("sex","age_group"), c("Gender","Age"))
dat[, Group:=paste(age_group, sex, sep = " ")]
dat[, `:=`(sex=NULL,age_group=NULL)]
```
## ============ PART 2
## Table2
## Make index summaries 
## Means and Standard Deviations for Age and Core Task Indices in Old and Young Groups

```{r}
library(compareGroups)
table2 <- descrTable(formula = Group ~ .,
                     data = dat)
```

```{r}
export2word(table2, "Table2.docx")
```

## ============ PART 3
## Table3
## Correlation Table

```{r}
library(apaTables)
apa.cor.table(data = dat[,2:8],
              filename = "Table3.doc",
              table.number = 3)
```
## ============ PART 4
## Table4
## The script for split-half reliability estimates is in another .R file named "wcst_index_calculation.R"
## ...


## ============ PART 5
## Figure3
## Gender and Age effect

```{r}
dat1 <- wcst[, .(subid, sex, age_group,age, Number_Correct, Number_PerseverativeResponse, Number_PerseverativeError, Number_NonPerseverativeError, Number_ConceptualLevelResponse, Number_Category, Number_FailureToMaintainSet)]

setnames(dat1, old = names(dat1)[5:11], c('TC', 'PR', 'PE', 'NPE', 'CLR', 'CAT', 'FMS'))

dat1[, sex:=factor(sex, levels = c("female","male"), labels = c("Female", "Male"))]
dat1[, age_group:=factor(age_group, levels = c("young","old"), labels = c("Young", "Old"))]
dat1[, subid:=factor(subid)]
```

### TC

```{r}
library(ez)
anova.TC <- ezANOVA(data = dat1,
                    dv = TC,
                    wid = subid,
                    between = .(sex, age_group),
                    type = 3)
anova.TC
apa.ezANOVA.table(anova.TC, table.title = "Anova on Total Correct", filename = "anova_TC.doc")
```

```{r}
anova.PR <- ezANOVA(data = dat1,
                    dv = PR,
                    wid = subid,
                    between = .(sex, age_group),
                    type = 3)
anova.PR
apa.ezANOVA.table(anova.PR, table.title = "Anova on Perseverative Response", filename = "anova_PR.doc")
```

```{r}
anova.PE <- ezANOVA(data = dat1,
                    dv = PE,
                    wid = subid,
                    between = .(sex, age_group),
                    type = 3)
anova.PE
apa.ezANOVA.table(anova.PE, table.title = "Anova on Perseverative Error", filename = "anova_PE.doc")
```

```{r}
anova.NPE <- ezANOVA(data = dat1,
                    dv = NPE,
                    wid = subid,
                    between = .(sex, age_group),
                    type = 3)
anova.NPE
apa.ezANOVA.table(anova.NPE, table.title = "Anova on Non-Perseverative Error", filename = "anova_NPE.doc")
```

```{r}
anova.CLR <- ezANOVA(data = dat1,
                    dv = CLR,
                    wid = subid,
                    between = .(sex, age_group),
                    type = 3)
anova.CLR
apa.ezANOVA.table(anova.CLR, table.title = "Anova on CLR", filename = "anova_CLR.doc")
```

```{r}
anova.CAT <- ezANOVA(data = dat1,
                    dv = CAT,
                    wid = subid,
                    between = .(sex, age_group),
                    type = 3)
anova.CAT
apa.ezANOVA.table(anova.CAT, table.title = "Anova on CAT", filename = "anova_CAT.doc")
```

```{r}
anova.FMS <- ezANOVA(data = dat1,
                    dv = FMS,
                    wid = subid,
                    between = .(sex, age_group),
                    type = 3)
anova.FMS
apa.ezANOVA.table(anova.FMS, table.title = "Anova on FMS", filename = "anova_FMS.doc")
```

### Using Linear Regression

```{r}
lm.TC <- lm(TC ~ sex*age_group, data = dat1)
summary(lm.TC)
```

## ============ PART 6
## Figure1
## Plot Age Group difference

```{r}
TC_diff <- dabest(.data = dat1,
                   x = age_group, 
                   y = TC,
                  idx = c("Young", "Old") ,
                   paired = FALSE) %>%
            cohens_d()
PR_diff <- dabest(.data = dat1,
                   x = age_group, 
                   y = PR,
                   idx = c("Young", "Old") ,
                   paired = FALSE) %>%
            cohens_d()
PE_diff <- dabest(.data = dat1,
                   x = age_group, 
                   y = PE,
                   idx = c("Young", "Old") ,
                   paired = FALSE) %>%
            cohens_d()
NPE_diff <- dabest(.data = dat1,
                   x = age_group, 
                   y = NPE,
                   idx = c("Young", "Old") ,
                   paired = FALSE) %>%
            cohens_d()
CLR_diff <- dabest(.data = dat1,
                   x = age_group, 
                   y = CLR,
                   idx = c("Young", "Old") ,
                   paired = FALSE) %>%
            cohens_d()
CAT_diff <- dabest(.data = dat1,
                   x = age_group, 
                   y = CAT,
                   idx = c("Young", "Old") ,
                   paired = FALSE) %>%
            cohens_d()
FMS_diff <- dabest(.data = dat1,
                   x = age_group, 
                   y = FMS,
                   idx = c("Young", "Old") ,
                   paired = FALSE) %>%
            cohens_d()
```

```{r}
fig_TC <- plot(TC_diff, effsize.ylabel = "Cohen's d")
fig_PR <- plot(PR_diff, effsize.ylabel = "Cohen's d")
fig_PE <- plot(PE_diff, effsize.ylabel = "Cohen's d")
fig_NPE <- plot(NPE_diff, effsize.ylabel = "Cohen's d")
fig_CLR <- plot(CLR_diff, effsize.ylabel = "Cohen's d")
fig_CAT <- plot(CAT_diff, effsize.ylabel = "Cohen's d")
fig_FMS <- plot(FMS_diff, effsize.ylabel = "Cohen's d")
```


```{r}
library(cowplot)
```

```{r}

fig_all <- plot_grid(fig_TC, fig_PR, fig_PE, fig_NPE, fig_CLR, fig_CAT, fig_FMS,
                     labels = "AUTO",
                     ncol = 3)

save_plot("age_difference.tiff", fig_all)
```


## Age continuous

```{r}
lm.old.TC <- lm(TC ~ sex+age, data = dat1[dat1$age_group == "Old"])
lm.old.PR <- lm(PR ~ sex+age, data = dat1[dat1$age_group == "Old"])
lm.old.PE <- lm(PE ~ sex+age, data = dat1[dat1$age_group == "Old"])
lm.old.NPE <- lm(NPE ~ sex+age, data = dat1[dat1$age_group == "Old"])
lm.old.CLR <- lm(CLR ~ sex+age, data = dat1[dat1$age_group == "Old"])
lm.old.CAT <- lm(CAT ~ sex+age, data = dat1[dat1$age_group == "Old"])
lm.old.FMS <- lm(FMS ~ sex+age, data = dat1[dat1$age_group == "Old"])
```


```
apa.reg.table(lm.old.TC, lm.old.PR, lm.old.PE, lm.old.NPE, lm.old.CLR, lm.old.CAT, lm.old.FMS,
              filename = "Old_Age_reg.doc")
```

```{r}
summary(lm.old.TC)
```

```{r}
summary(lm.old.PR)
```

```{r}
summary(lm.old.PE)
```

```{r}
summary(lm.old.NPE)
```

```{r}
summary(lm.old.CLR)
```

```{r}
summary(lm.old.CAT)
```


```{r}
summary(lm.old.FMS)
```

```{r}
lm.young.TC <- lm(TC ~ sex+age, data = dat1[dat1$age_group == "Young"])
lm.young.PR <- lm(PR ~ sex+age, data = dat1[dat1$age_group == "Young"])
lm.young.PE <- lm(PE ~ sex+age, data = dat1[dat1$age_group == "Young"])
lm.young.NPE <- lm(NPE ~ sex+age, data = dat1[dat1$age_group == "Young"])
lm.young.CLR <- lm(CLR ~ sex+age, data = dat1[dat1$age_group == "Young"])
lm.young.CAT <- lm(CAT ~ sex+age, data = dat1[dat1$age_group == "Young"])
lm.young.FMS <- lm(FMS ~ sex+age, data = dat1[dat1$age_group == "Young"])
```

```{r}
summary(lm.young.TC)
```

```{r}
summary(lm.young.PR)
```

```{r}
summary(lm.young.PE)
```

```{r}
summary(lm.young.NPE)
```


```{r}
summary(lm.young.CLR)
```

```{r}
summary(lm.young.CAT)
```

```{r}
summary(lm.young.FMS)
```

## Education 

```{r}
dat2 <- wcst[, .(sex, age_group,age, cultural, Number_Correct, Number_PerseverativeResponse, Number_PerseverativeError, Number_NonPerseverativeError, Number_ConceptualLevelResponse, Number_Category, Number_FailureToMaintainSet)]

setnames(dat2, old = names(dat2)[5:11], c('TC', 'PR', 'PE', 'NPE', 'CLR', 'CAT', 'FMS'))
setnames(dat2, old = "cultural", "edu")
dat2[, sex:=factor(sex, levels = c("female","male"), labels = c("Female", "Male"))]
dat2[, age_group:=factor(age_group, levels = c("young","old"), labels = c("Young", "Old"))]
set(dat2, i = which(dat2$edu==0), j = which(names(dat2)=="edu"), 1)
```


```{r}
lm.old.TC.edu <- lm(TC ~ edu + sex*age, data = dat2[dat2$age_group=="Old"])
summary(lm.old.TC.edu)
```

```{r}
lm.old.PE.edu <- lm(PE ~ edu + sex + age, data = dat2[dat2$age_group=="Old"])
summary(lm.old.PE.edu)
```

```{r}
lm2.old.TC <- lm(TC ~ edu+sex+age, data = dat2[dat2$age_group == "Old"])
lm2.old.PR <- lm(PR ~ edu+sex+age, data = dat2[dat2$age_group == "Old"])
lm2.old.PE <- lm(PE ~ edu+sex+age, data = dat2[dat2$age_group == "Old"])
lm2.old.NPE <- lm(NPE ~ edu+sex+age, data = dat2[dat2$age_group == "Old"])
lm2.old.CLR <- lm(CLR ~ edu+sex+age, data = dat2[dat2$age_group == "Old"])
lm2.old.CAT <- lm(CAT ~ edu+sex+age, data = dat2[dat2$age_group == "Old"])
lm2.old.FMS <- lm(FMS ~ edu+sex+age, data = dat2[dat2$age_group == "Old"])
```

```{r}
summary(lm2.old.TC)
```

```{r}
summary(lm2.old.PR)
```

```{r}
summary(lm2.old.PE)
```

```{r}
summary(lm2.old.CAT)
```

```{r}
summary(lm2.old.TC)
```

```{r}
summary(lm2.old.NPE)
```

```{r}
summary(lm2.old.FMS)
```

```{r}
summary(lm2.old.CLR)
```



```{r}
old <- dat2[age_group=="Old"]
old[, edu:=factor(edu)]
setnames(old, "sex", "Gender")
setnames(old, "edu", "Education")
f1 <- ggplot(old, aes(age, CAT, color=Gender)) +
  geom_point(aes(shape=Education), position = position_jitter()) +
  geom_smooth(method="lm", formula="y~x") +
  scale_y_continuous(breaks = c(0,1,2,3,4,5)) +
  scale_x_continuous(breaks = c(55, 60, 65, 70, 75, 80)) +
  coord_fixed(ratio = 5) +
  labs(x="Age (Years)", y = "Category Completed (CAT)") +
  theme_cowplot() +
  panel_border() +
  theme(legend.position = "right")
print(f1)
```

```{r}
save_plot("RegressionPlot.tiff", plot = f1)
```





```{r}
summary(lm2.old.CLR)
```

```{r}
summary(lm2.old.FMS)
```

```{r}
summary(lm2.old.NPE)
```

```{r}
lm2.young.TC <- lm(TC ~ edu+sex+age, data = dat2[dat2$age_group == "Young"])
lm2.young.PR <- lm(PR ~ edu+sex+age, data = dat2[dat2$age_group == "Young"])
lm2.young.PE <- lm(PE ~ edu+sex+age, data = dat2[dat2$age_group == "Young"])
lm2.young.NPE <- lm(NPE ~ edu+sex+age, data = dat2[dat2$age_group == "Young"])
lm2.young.CLR <- lm(CLR ~ edu+sex+age, data = dat2[dat2$age_group == "Young"])
lm2.young.CAT <- lm(CAT ~ edu+sex+age, data = dat2[dat2$age_group == "Young"])
lm2.young.FMS <- lm(FMS ~ edu+sex+age, data = dat2[dat2$age_group == "Young"])
```

```{r}
summary(lm2.young.CAT)
```

```{r}
summary(lm2.young.PE)
```










